---
title: "reading_data_from_web"
author: "Yingyu Cui"
date: "2024-10-18"
output: github_document
---

```{r setup and figure preferrences}
library(tidyverse)

library(rvest)
library(httr)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```
## Scrape a table from a webpage
I want the first table from [this page](https://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm)

read in the html
```{r read the html}
url = "https://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"

drug_use_html = read_html(url)
```

extract the table, but only focus on the first one
```{r extract the table}
table_marj =
  drug_use_html |> 
  html_table() |> 
  first() |> 
  slice(-1) |> 
  as_tibble()
table_marj
```

assessment1
most the cases, we should add the header = TRUE to the html_table() function to get the correct table. 
```{r assessment1 html read}
url1 = "https://www.bestplaces.net/cost_of_living/city/new_york/new_york"

NYC_cost_html = read_html(url1)
```
```{r assessment1 extract the table}
table_NYC_cost = 
  NYC_cost_html |> 
  html_table (header = TRUE) |> 
  first()
```


## star war movies info

I want some data from [here]("https://www.imdb.com/list/ls070150896/")
```{r read the html}
url2 = "https://www.imdb.com/list/ls070150896/"
swm_html = read_html(url2)
```

get some elements from the page
```{r extract the elements}
title_vec = 
  swm_html |>
  html_elements(".ipc-title-link-wrapper .ipc-title__text") |>
  html_text()

metascore_vec = 
  swm_html |>
  html_elements(".metacritic-score-box") |>
  html_text()

runtime_vec = 
  swm_html |>
  html_elements(".dli-title-metadata-item:nth-child(2)") |>
  html_text()

swm_df = 
  tibble(
    title = title_vec,
    score = metascore_vec,
    runtime = runtime_vec)
```

assessment2
```{r assessment2}
url3 = "https://books.toscrape.com/"
books_html = read_html(url3)

titles = 
  books_html |>
  html_elements("h3") |>
  html_text()

stars = 
  books_html |>
  html_elements(".star-rating") |>
  html_text()
```

## API functions
request the server about some data 
```{r data }
nyc_water = 
  GET("https://data.cityofnewyork.us/resource/ia2d-e54m.csv") |> 
  content("parsed")
```
or we could use the json format
```{r data2}
nyc_water_json = 
  GET("https://data.cityofnewyork.us/resource/ia2d-e54m.json") |> 
  content("text") |> 
  jsonlite::fromJSON() |>
  as_tibble()
```

GET("https://chronicdata.cdc.gov/resource/acme-vg9e.csv",
      query = list("$limit" = 5000))
query function:
about how many rows are requested from the server 

